### 2017-07-07 motivation.tex
Edits to Sec. 2.

We present our ideas in the context of an embedded DSL in OCaml that
we have developed which supports a \C{DB} monad to define and compose
database computations given in terms of SQL operations.  Besides the
usual \C{bind} and \C{return} operators, the monad offers an
\C{atomically} combinator that executes a database computation as an
atomic transaction and returns the result.

@@

Fig.~\ref{fig:new_order_code} shows a simplified version of the TPC-C
\C{new\_order} transaction written in this language.  TPC-C is a
well-known Online Transaction Processing (OLTP) benchmark that models
an order-processing system for a wholesale parts supply business. The
business logic is captured in 5 database transactions that operate on
9 tables; \C{new\_order} is one such transaction that uses
\C{District}, \C{Order}, \C{New\_order}, \C{Stock}, and
\C{Order\_line} tables. The transaction acts on the behalf of a
customer, whose id is \C{c\_id}, to place a new order for a given
set of items (\C{item\_reqs}), to be served by a warehouse under the
district identified by \C{d\_id}.  Fig.~\ref{fig:schema} illustrates
the relationship among these different tables.

@@

\begin{figure}[!t]
\includegraphics[scale=0.5]{Figures/schema}
\caption{Database schema of TPC-C's order management system.
  Columns against highlighted background are primary keys. Arrows denote
  foreign key relationships.}
\label{fig:schema}
\end{figure}

>>>>

We present our ideas in the context of our DSL embedded in OCaml,
which offers a \C{DB} monad to define and compose database
computations given in terms of SQL operations.  Besides the usual
\C{bind} and \C{return} operators, the monad offers an \C{atomically}
combinator that executes a database computation as an atomic
transaction and returns the result.

@@

Fig.~\ref{fig:new_order_code} shows a simplified version of the TPC-C
\C{new\_order} transaction written in this language. TPC-C is a
widely-used Online Transaction Processing (OLTP) benchmark that models
an order-processing system for a wholesale parts supply business. The
business logic is captured in 5 database transactions that operate on
9 tables; \C{new\_order} is one such transaction that uses
\C{District}, \C{Order}, \C{New\_order}, \C{Stock}, and
\C{Order\_line} tables. The transaction acts on the behalf of a
customer, whose id is \C{c\_id}, to place a new order for a given
set of items (\C{item\_reqs}), to be served by a warehouse under the
district identified by \C{d\_id}.  Fig.~\ref{fig:schema} illustrates
the relationship among these different tables.

@@

% \begin{figure}[!t]
% \includegraphics[scale=0.5]{Figures/schema}
% \caption{Database schema of TPC-C's order management system.
%   Columns against highlighted background are primary keys. Arrows denote
%   foreign key relationships.}
% \label{fig:schema}
% \end{figure}

\begin{figure}[t]
  \centering
	\begin{subfigure}{0.48\textwidth}
		\includegraphics[width=0.9\textwidth]{Figures/schema1}
    \caption{A valid TPC-C database. The only existing order belongs
      to the district with \C{d\_id}=11. It's id (\C{o\_id}) is one
      less than the district's \C{d\_next\_o\_id}, and it's order
      count (\C{o\_ol\_cnt}) is equal to the number of order line
      records whose \C{ol\_o\_id} is equal to the order's id.  }
		\label{fig:tpcc_db1}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\includegraphics[width=0.9\textwidth]{Figures/schema2}
    \caption{The database in Fig.~\ref{fig:tpcc_db1} after correctly
      executing a \C{new\_order} transaction. A new order record is
      added whose \C{o\_id} is equal to the \C{d\_next\_o\_id} from
      Fig.~\ref{fig:tpcc_db1}. The district's \C{d\_next\_o\_id} is
      incremented. The order's \C{o\_ol\_cnt} is 2, reflecting the
      actual number of order line records whose \C{ol\_o\_id} is equal
      to the order's id (2).}
		\label{fig:tpcc_db2}
	\end{subfigure}

\caption{Database schema of TPC-C's order management system.
  The naming
  convention indicates primary keys and foreign keys. For e.g.,
  \C{ol\_id} is the primary key column of the order line table,
  whereas \C{ol\_o\_id} is a foreign key that refers to the \C{o\_id}
  column of the order table.}
\label{fig:schema}
\end{figure}
